Missing data in sports science: Current practice in football research and recommendations for reporting missingness

### 2020-08-28 paper/paper.Rmd
remove a space
add supplement headings

---
title: "Missing data in sports science: Current practice in football research and recommendations for reporting missingness"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
bibliography: references.bib
---

@@

@@

It is imperative that missing data (or lack thereof -- Absence of
evidence is not evidence of absence) are reported. However, outside of
sports science, researchers seldom consider missing data [@Schafer2002].
Moreover, while there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missing data have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several bad missing data practices; and (3) provide recommendations for
exploring and reporting missingness.

@@

>>>>

---
title: "Missing data in sports science: Current practice in football research and recommendations for reporting missingness"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

**Word count**

```{r count-words}
wordcountaddin::text_stats()
```

@@

It is imperative that missing data (or lack thereof --Absence of
evidence is not evidence of absence) are reported. However, outside of
sports science, researchers seldom consider missing data [@Schafer2002].
Moreover, while there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missing data have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several bad missing data practices; and (3) provide recommendations for
exploring and reporting missingness.

@@

# Supplement 1

# Supplement 2

# Supplement 3
